---
title: "Cleaning Script"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Package Loading

```{r}
library(tidyverse)
```

# Data Loading

```{r}
stakeholder_survey <- read.csv("/Users/kenjinchang/github/scr-and-stakeholder-analysis/data/survey-data.csv")
```

# Cleaning

First, we will need to select and rename the variables relevant to our plan of analysis. We will specifically focus on the following: 

* `date`, which corresponds to the date and time the response was recorded
* `completion`, which corresponds to the proportion of the survey that was completed
* `channel`, which corresponds to the means through which the survey materials were accessed
* `consent`, which corresponds to whether participants provided informed consent 
* `involvement`, which corresponds to the participants' self-reported role in deciding dining policies and practices
* `involvement_other`, which corresponds to to offered clarifications on participants' reported roles in deciding dining policies and practices
* `stakeholder_type`, which corresponds to the type of professional role participants reported as serving
* `stakeholder_type_other`, which corresponds to offered clarifications on the type of professional role participants reported as serving
* `title`, which corresponds to participants' disclosed job titles
* `role_duration`, which corresponds to the number of years participants have served in that position
* `dietary_health_ranking`, which corresponds to the level of priority given to the healthiness of food offerings
* `dietary_sustainability_ranking`, which corresponds to the level of priority given to the sustainability of guest food choices
* `institutional_sustainability_ranking`, which corresponds to the level of priority given to the sustainability of dining operations
* `food_pricing_ranking`, which corresponds to the level of priority given to the campus food prices
* `operational_costs_ranking`, which corresponds to the level of priority given to cost of funding dining operations
* `guest_satisfaction_ranking`, which corresponds to the level of priority given to the dining experiences of students
* `worker_satisfaction_ranking`, which corresponds to the level of priority given to the labor experiences of dining staff
* `campus_culture_ranking`, which corresponds to the level of priority given to campus sustainability culture and the monitoring of spillover effects
* `other_ranking`, which corresponds to the level of priority given to other relevant indicators of university-based dietary intervention performance not considered in the provided list
* `other_ranking_other`, which corresponds to offered indicators

```{r}
stakeholder_survey <- stakeholder_survey %>%
  select(RecordedDate,Progress,DistributionChannel,Q1,Q2,Q2_4_TEXT,Q6,Q6_10_TEXT,Q3,Q5_1,Q2_1,Q2_2,Q2_3,Q2_4,Q2_5,Q2_6,Q2_7,Q2_8,Q2_9,Q2_9_TEXT) %>%
  rename(date=RecordedDate,completion=Progress,channel=DistributionChannel,consent=Q1,involvement=Q2,involvement_other=Q2_4_TEXT,stakeholder_type=Q6,stakeholder_type_other=Q6_10_TEXT,title=Q3,role_duration=Q5_1,dietary_health_ranking=Q2_1,dietary_sustainability_ranking=Q2_2,institutional_sustainability_ranking=Q2_3,food_pricing_ranking=Q2_4,operational_costs_ranking=Q2_5,guest_satisfaction_ranking=Q2_6,worker_satisfaction_ranking=Q2_7,campus_culture_ranking=Q2_8,other_ranking=Q2_9,other_ranking_other=Q2_9_TEXT) 
```

We also need to (1) omit the first three rows, which contain information about how the survey variables are coded and (2) reclass the `dietary_health_ranking`, `dietary_sustainability_ranking`, `institutional_sustainability_ranking`, `food_price_ranking`, `operational_costs_ranking`, `guest_satisfaction_ranking`, `worker_satisfaction_ranking`, `campus_culure_ranking`, and `other_ranking` variables from characteric strings to numeric vectors. 

```{r}
stakeholder_survey <- stakeholder_survey %>%
  slice(3:n()) %>%
  mutate(dietary_health_ranking=as.numeric(dietary_health_ranking)) %>%
  mutate(dietary_sustainability_ranking=as.numeric(dietary_sustainability_ranking)) %>%
  mutate(institutional_sustainability_ranking=as.numeric(institutional_sustainability_ranking)) %>%
  mutate(food_pricing_ranking=as.numeric(food_pricing_ranking)) %>%
  mutate(operational_costs_ranking=as.numeric(operational_costs_ranking)) %>%
  mutate(guest_satisfaction_ranking=as.numeric(guest_satisfaction_ranking)) %>%
  mutate(worker_satisfaction_ranking=as.numeric(worker_satisfaction_ranking)) %>%
  mutate(campus_culture_ranking=as.numeric(campus_culture_ranking)) %>%
  mutate(other_ranking=as.numeric(other_ranking)) 
```

With this complete, we can now move on to address an isolated difference in how one subject elected to respond to the rank-order choice set. More specifically, this participant used the provided prompt to suggest an unlisted performance indicator in `other_ranking_other`, with all other respondents ranking `other_ranking` last and without any additional details. Given this, in the interest of constructing a consistent scoring system, we will narratively note the omission of the suggested "Cuisine type" indicator in our results while simultaneously removing the `other_ranking` and `other_ranking_other` variables from the variable list. 

In this particular instance, because the subject identified this previously unspecified indicator with a rank of "2," this requires us to subtract 1 from every ranked indicator apart from `guest_satisfaction_ranking`, which was ranked first, ahead of "Cuisine type."

To accomplish this, we will first transform the data by adding variable `id` to attach unique identifiers to each individual response. This will help us isolate the changes in ranking to the one outlying response set.

```{r}
stakeholder_survey <- stakeholder_survey %>%
  mutate(id=row_number())
```


Now, we move on to the next step, which involves recoding all rank responses greater than "2," such that every performance indicator apart from `guest_satisfaction_ranking` moves one position ahead to compensate for the joint removal of `other_ranking` and `other_ranking_other`.

```{r}
stakeholder_survey <- stakeholder_survey %>%
  mutate(campus_culture_ranking=case_when(id == 22 ~ 8,
                                          TRUE ~ campus_culture_ranking)) %>%
  mutate(worker_satisfaction_ranking=case_when(id == 22 ~ 7,
                                          TRUE ~ worker_satisfaction_ranking)) %>%
  mutate(operational_costs_ranking=case_when(id == 22 ~ 2,
                                          TRUE ~ worker_satisfaction_ranking)) %>%
  mutate(food_pricing_ranking=case_when(id == 22 ~ 3,
                                          TRUE ~ food_pricing_ranking)) %>%
  mutate(institutional_sustainability_ranking=case_when(id == 22 ~ 4,
                                          TRUE ~ institutional_sustainability_ranking)) %>%
  mutate(dietary_sustainability_ranking=case_when(id == 22 ~ 5,
                                          TRUE ~ dietary_sustainability_ranking)) %>%
  mutate(dietary_health_ranking=case_when(id == 22 ~ 6,
                                          TRUE ~ dietary_health_ranking)) 
```

With 

```{r}
stakeholder_survey %>% select(-other_ranking,-other_ranking_other)
```

Inverted scoring system

```{r}
stakeholder_survey <- stakeholder_survey %>%
  mutate(dietary_health_score=case_when(dietary_health_ranking == 1 ~ 8,
                                        dietary_health_ranking == 2 ~ 7,
                                        dietary_health_ranking == 3 ~ 6,
                                        dietary_health_ranking == 4 ~ 5,
                                        dietary_health_ranking == 5 ~ 4,
                                        dietary_health_ranking == 6 ~ 3,
                                        dietary_health_ranking == 7 ~ 2,
                                        dietary_health_ranking == 8 ~ 1)) %>%
  mutate(dietary_sustainability_score=case_when(dietary_sustainability_ranking == 1 ~ 8,
                                        dietary_sustainability_ranking == 2 ~ 7,
                                        dietary_sustainability_ranking == 3 ~ 6,
                                        dietary_sustainability_ranking == 4 ~ 5,
                                        dietary_sustainability_ranking == 5 ~ 4,
                                        dietary_sustainability_ranking == 6 ~ 3,
                                        dietary_sustainability_ranking == 7 ~ 2,
                                        dietary_sustainability_ranking == 8 ~ 1)) %>%
  mutate(institutional_sustainability_score=case_when(institutional_sustainability_ranking == 1 ~ 9,
                                        institutional_sustainability_ranking == 2 ~ 8,
                                        institutional_sustainability_ranking == 3 ~ 7,
                                        institutional_sustainability_ranking == 4 ~ 6,
                                        institutional_sustainability_ranking == 5 ~ 5,
                                        institutional_sustainability_ranking == 6 ~ 4,
                                        institutional_sustainability_ranking == 7 ~ 3,
                                        institutional_sustainability_ranking == 8 ~ 2,
                                        institutional_sustainability_ranking == 9 ~ 1)) %>%
  mutate(food_pricing_score=case_when(food_pricing_ranking == 1 ~ 8,
                                        food_pricing_ranking == 2 ~ 7,
                                        food_pricing_ranking == 3 ~ 6,
                                        food_pricing_ranking == 4 ~ 5,
                                        food_pricing_ranking == 5 ~ 4,
                                        food_pricing_ranking == 6 ~ 3,
                                        food_pricing_ranking == 7 ~ 2,
                                        food_pricing_ranking == 8 ~ 1)) %>%
  mutate(operational_costs_score=case_when(operational_costs_ranking == 1 ~ 8,
                                        operational_costs_ranking == 2 ~ 7,
                                        operational_costs_ranking == 3 ~ 6,
                                        operational_costs_ranking == 4 ~ 5,
                                        operational_costs_ranking == 5 ~ 4,
                                        operational_costs_ranking == 6 ~ 3,
                                        operational_costs_ranking == 7 ~ 2,
                                        operational_costs_ranking == 8 ~ 1)) %>%
  mutate(guest_satisfaction_score=case_when(guest_satisfaction_ranking == 1 ~ 8,
                                        guest_satisfaction_ranking == 2 ~ 7,
                                        guest_satisfaction_ranking == 3 ~ 6,
                                        guest_satisfaction_ranking == 4 ~ 5,
                                        guest_satisfaction_ranking == 5 ~ 4,
                                        guest_satisfaction_ranking == 6 ~ 3,
                                        guest_satisfaction_ranking == 7 ~ 2,
                                        guest_satisfaction_ranking == 8 ~ 1)) %>%
  mutate(worker_satisfaction_score=case_when(worker_satisfaction_ranking == 1 ~ 8,
                                        worker_satisfaction_ranking == 2 ~ 7,
                                        worker_satisfaction_ranking == 3 ~ 6,
                                        worker_satisfaction_ranking == 4 ~ 5,
                                        worker_satisfaction_ranking == 5 ~ 4,
                                        worker_satisfaction_ranking == 6 ~ 3,
                                        worker_satisfaction_ranking == 7 ~ 2,
                                        worker_satisfaction_ranking == 8 ~ 1)) %>%
  mutate(campus_culture_score=case_when(campus_culture_ranking == 1 ~ 8,
                                        campus_culture_ranking == 2 ~ 7,
                                        campus_culture_ranking == 3 ~ 6,
                                        campus_culture_ranking == 4 ~ 5,
                                        campus_culture_ranking == 5 ~ 4,
                                        campus_culture_ranking == 6 ~ 3,
                                        campus_culture_ranking == 7 ~ 2,
                                        campus_culture_ranking == 8 ~ 1)) %>%
  mutate(other_score=case_when(other_ranking == 1 ~ 8,
                                        other_ranking == 2 ~ 7,
                                        other_ranking == 3 ~ 6,
                                        other_ranking == 4 ~ 5,
                                        other_ranking == 5 ~ 4,
                                        other_ranking == 6 ~ 3,
                                        other_ranking == 7 ~ 2,
                                        other_ranking == 8 ~ 1)) 
```


```{r}
stakeholder_survey %>%
  group_by(involvement) %>%
  summarise(dietary_health_score_mean=mean(dietary_health_score),dietary_sustainability_score_mean=mean(dietary_sustainability_score),institutional_sustainability_score_mean=mean(institutional_sustainability_score),institutional_sustainability_score_mean=mean(institutional_sustainability_score),food_pricing_score_mean=mean(food_pricing_score),operational_costs_score_mean=mean(operational_costs_score),guest_satisfaction_score_mean=mean(guest_satisfaction_score),worker_satisfaction_score_mean=mean(worker_satisfaction_score),campus_culture_score_mean=mean(campus_culture_score),other_score_mean=mean(other_score),n=n())
```

```{r}
stakeholder_survey %>%
  group_by(stakeholder_type) %>%
  summarise(dietary_health_score_mean=mean(dietary_health_score),dietary_sustainability_score_mean=mean(dietary_sustainability_score),institutional_sustainability_score_mean=mean(institutional_sustainability_score),institutional_sustainability_score_mean=mean(institutional_sustainability_score),food_pricing_score_mean=mean(food_pricing_score),operational_costs_score_mean=mean(operational_costs_score),guest_satisfaction_score_mean=mean(guest_satisfaction_score),worker_satisfaction_score_mean=mean(worker_satisfaction_score),campus_culture_score_mean=mean(campus_culture_score),other_score_mean=mean(other_score),n=n())
```

```{r}
stakeholder_survey %>%
  summarise(dietary_health_score_mean=mean(dietary_health_score),dietary_sustainability_score_mean=mean(dietary_sustainability_score),institutional_sustainability_score_mean=mean(institutional_sustainability_score),institutional_sustainability_score_mean=mean(institutional_sustainability_score),food_pricing_score_mean=mean(food_pricing_score),operational_costs_score_mean=mean(operational_costs_score),guest_satisfaction_score_mean=mean(guest_satisfaction_score),worker_satisfaction_score_mean=mean(worker_satisfaction_score),campus_culture_score_mean=mean(campus_culture_score),other_score_mean=mean(other_score),n=n())
```
```{r}
stakeholder_survey %>%
  summarise(dietary_health_score_sum=sum(dietary_health_score),dietary_sustainability_score_sum=sum(dietary_sustainability_score),institutional_sustainability_score_sum=sum(institutional_sustainability_score),institutional_sustainability_score_sum=sum(institutional_sustainability_score),food_pricing_score_sum=sum(food_pricing_score),operational_costs_score_sum=sum(operational_costs_score),guest_satisfaction_score_sum=sum(guest_satisfaction_score),worker_satisfaction_score_sum=sum(worker_satisfaction_score),campus_culture_score_sum=sum(campus_culture_score),other_score_sum=sum(other_score),n=n())
```
